

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\begin{thebibliography}{AMM08a}


\bibitem{AIMcat} AIM Minimum Rank Graph Catalog.  
\url{http://www.aimath.org/data/paper/AIM08/}


\bibitem{AIM} AIM Minimum Rank -- Special Graphs Work Group 
(F. Barioli, W. Barrett, 
S. Butler,   
S. M. Cioaba, D. Cvetkovi\'c, 
 S. M. Fallat,
C. Godsil,  
W. Haemers,  
L. Hogben,  R. Mikkelson,  S. Narayan,  O. Pryporova,   
I. Sciriha,  W. So,   D. Stevanovi\'c,  H. van der Holst,
K. Vander Meulen, and
A. Wangsness).  Zero forcing sets and the minimum rank  
of graphs.   {\em Lin. Alg. Appl.}, 
428: 1628--1648, 2008.


\bibitem{estrella} E. Almodovar, L. DeLoss, L. Hogben, 
K. Hogenson, K. Murphy, T. Peters, and C. Ram\'irez. Minimum 
rank, maximum nullity and zero forcing number, and spreads 
of these parameters for selected graph families. 
 {\em Involve}, 3: 371--392, 2010.


\bibitem{AIM06} American Institute of Mathematics workshop,
``Spectra of Families of Matrices described by Graphs, Digraphs, 
and Sign Patterns,"
held Oct. 23-27, 2006 in Palo Alto, CA. \url{http://aimath.org/pastworkshops/matrixspectrum.html}



\bibitem{NGsurvey13}	M. Aouchiche and P. Hansen. A survey of Nordhaus--Gaddum type relations.  
{\em Disc. Appl. Math.}, 161: 466--546, 2013.



\bibitem{AHKLR} M. Arav, F. Hall, S. Koyuncu, Z. Li, and B. Rao.
Rational realizations of the minimum rank of a sign pattern matrix.
{\em Lin. Alg. Appl.}, 409: 111--125, 2005.

\bibitem{AHL} M. Arav, F. Hall, Z. Li, A. Merid, and Y. Gao.
Sign patterns that require almost unique rank.
{\em Lin. Alg. Appl.}, 430: 7--16, 2009.




\bibitem{smallparam}	F. Barioli, W. Barrett, S. Fallat, H.T. Hall, 
L. Hogben, B. Shader, P. van den Driessche, and H. van der Holst.  
Zero forcing parameters and minimum rank problems.  
{\em Lin. Alg. Appl.}, 433: 401--411, 2010.



\bibitem{GCC}		F. Barioli, W. Barrett, S. Fallat, 
H.T. Hall, L. Hogben, and H. van der Holst. 
On the graph complement conjecture associated with minimum rank.
{\em Lin. Alg. Appl.}, 436: 4373--4391, 2012.

\bibitem{param}	F. Barioli, W. Barrett, S. Fallat, H.T. Hall, 
L. Hogben, B. Shader, P. van den Driessche, and H. van der Holst.  
Parameters related to tree-width, zero forcing, and maximum 
nullity of a graph.  {\em J. Graph Theory}, 72: 146--177, 2013.

\bibitem{BF} F. Barioli and S.M. Fallat.
On the minimum rank of the join of graphs and decomposable graphs.
{\em Lin. Alg. Appl.}, 421: 252--263, 2007.

\bibitem{square1} F. Barioli, S.M. Fallat,  H.T. Hall, 
D. Hershkowitz, L. Hogben, H. van der Holst, and B. Shader.
   On the minimum rank of not necessarily symmetric matrices: 
   a preliminary study.
   {\em Elec. J.  Lin. Alg.}, 18: 126--145, 2009.
  
\bibitem{BFH} F. Barioli, S.M. Fallat, and L. Hogben.
\newblock Computation of minimal rank and path cover number for graphs.
\newblock {\em Lin. Alg. Appl.},
392: 289--303, 2004. 

\bibitem{BFH2} F. Barioli, S.M. Fallat, and L. Hogben.
\newblock On the difference between the maximum multiplicity and path cover number for
tree-like graphs.
\newblock  {\em Lin. Alg. Appl.} 409: 13--31, 2005.  

\bibitem{BFH3}	F. Barioli, S.M. Fallat, and L. Hogben.
\newblock A variant on the graph parameters of Colin de Verdi\`ere:
Implications to the minimum rank of graphs.
\newblock {\em Elec. J.  Lin. Alg.},
13: 387--404, 2005.    

\bibitem{BFMN}
F. Barioli, S. Fallat, L. Mitchell, and S. Narayan,
Minimum semidefinite rank of outerplanar graphs and the tree cover number.
{\em Elec. J.  Lin. Alg.},  22: 10--21, 2011.


\bibitem{BFS} F. Barioli,  S.M. Fallat, and R.L. Smith. On acyclic 
and unicyclic graphs whose minimum rank equals the diameter. 
{\em Lin. Alg. Appl.},  429: 1568--1578, 2008. 


\bibitem{BetalSubdiv} W. Barrett, R. Bowcutt, M.  Cutler, S. Gibelyou, 
and K. Owens. Minimum rank of edge subdivisions of graphs. {\em Elec. J.  Lin. Alg.},  18: 530--563, 2009.


\bibitem{MZsubdiv}		 W. Barrett, S. Butler, M. Catral, S. Fallat, 
H.T. Hall, L. Hogben,  and M. Young.
The maximum nullity of a complete subdivision graph is equal to its zero forcing number, $\M(\sdg G)=\ZFS(\sdg G)$.
Under review.


\bibitem{BGL} W.  Barrett, J. Grout, and R. Loewy. The minimum rank problem 
over the finite field of order 2: minimum rank 3. 
{\em Lin. Alg. Appl.}, 430: 890--923, 2009.


\bibitem{BHL09} W.  Barrett, H.T. Hall, and R. Loewy. The inverse inertia 
problem for graphs: Cut vertices, trees,
and a counterexample. {\em Lin. Alg. Appl.}, 
431: 1147--1191, 2009.


\bibitem{BHL04} W.W. Barrett, H. van der Holst, and R. Loewy. Graphs 
whose minimal rank is two. \emph{Elec. J.  Lin. Alg.}, 
11: 258-280, 2004.


\bibitem{BHL05} 	W. Barrett, H. van der Holst, and R. Loewy. 
\newblock Graphs whose minimal rank is two: The finite fields case. 
\newblock {\em Elec. J.  Lin. Alg.},
14: 32--42, 2005. 


\bibitem{Betal} W. Barrett, C. Jepsen, R. Lang, E. McHenry, C. Nelson, and
K. Owens. Inertia sets for graphs on six or fewer vertices.  
{\em Elec. J.  Lin. Alg.}, 20: 53--78, 2010.


\bibitem{BLD} A. Bento and A. Leal-Duarte.
    On Fiedler's characterization of tridiagonal matrices over
    arbitrary fields.
    {\em Lin. Alg. Appl.}, 401: 467--481, 2005.


\bibitem{QRC} A. Berman, S. Friedland,  L. Hogben, 
U.G. Rothblum, and B.  Shader. Minimum rank of matrices described 
by a graph or pattern over the rational, real and complex numbers.   
{\em Elec. J. Comb.}, 15: Research Paper 25 
(19 pp.), 2008. 


\bibitem{delta} A. Berman, S. Friedland,  L. Hogben, U.G. Rothblum, 
and B. Shader.    An upper bound for the minimum rank of a graph. 
{\em Lin. Alg. Appl.}, 429: 1629--1638, 2008.


\bibitem{psdrank}
M. Booth, P. Hackney, B. Harris, C.R. Johnson, M. Lay, T.D. Lenker, L.H. Mitchell, S.K. Narayan, A. Pascoe, and B.D. Sutton.
On the minimum semidefinite rank of a simple graph.
{\em Lin. Multilin. Alg.}, 59: 483--506, 2011.


\bibitem{Netal08chord} M. Booth, P. Hackney, B. Harris, C.R. Johnson, 
M. Lay, L.H. Mitchell, S.K. Narayan,
A. Pascoe, K. Steinmetz, B.D. Sutton, and W. Wang. On the minimum rank 
among positive semidefinite
matrices with a given graph. 
{\em SIAM J.  Matrix Anal. and Appl.}, 
30: 731--740, 2008.


\bibitem{BCS} R.A. Brualdi, K.L. Chavey, and B.L. Shader.
Rectangular L-matrices. {\em Lin. Alg. Appl.}, 196: 37--61, 1994.


\bibitem{AIMrpt} R. Brualdi, L. Hogben, and B. Shader. 
AIM Workshop on Spectra of Families of Matrices Described by Graphs, 
Digraphs and Sign
Patterns, Final report: Mathematical Results, 2007. 
\url{http://aimath.org/pastworkshops/matrixspectrumrep.pdf}.


\bibitem{ZFQC} D. Burgarth, D. D'Alessandro, L. Hogben, S. Severini, and M. Young.
Zero forcing, linear and quantum controllability for systems evolving on networks.   {\em IEEE Trans. Auto. Control}, 58: 2349 -- 2354, 2013. 


\bibitem{graphinfect} D. Burgarth and V. Giovannetti. 
Full control by locally induced relaxation. {\em Phys. Rev. Lett.} 
PRL 99, 100--501, 2007.



\bibitem{mrsage}	S. Butler, L. DeLoss, J. Grout, H.T. Hall, J. LaGrange, 
T. McKay, J. Smith, and G. Tims.
Minimum Rank Library (\sage ~programs for calculating bounds on 
the minimum rank of a graph, and for computing zero forcing parameters).  
Available  at \url{http://sage.cs.drake.edu/home/pub/67/}. 
For more information contact Jason Grout at \url{jason.grout@drake.edu}.


\bibitem{CJ} 	R. Cant\'o and C.R. Johnson. The relationship between 
maximum triangle size and minimum rank for zero-nonzero patterns.  
{\em Textos de Matematica}, 39: 39--48, 2006.


\bibite{REU11} M. Catral, A. Cepek, L. Hogben, M. Huynh, K. Lazebnik, T. Peters, and M. Young.
   Zero forcing number, maximum nullity,  and path cover number of  subdivided  graphs
   {\em Elec. J.  Lin. Alg.}, 23: 906--922, 2012.

\bibitem{CN71} G. Chartrand and J. Mitchem.  
Graphical theorems of the Nordhaus-Gaddum class.   
In {\em Recent Trends in Graph Theory}, pp. 55Ð61, 
Springer, Berlin, 1971.


\bibitem{CDH07} 	N.L. Chenette, S.V. Droms, L. Hogben, R. Mikkelson, and O. Pryporova. 
 Minimum rank of a tree over an arbitrary field. 
{\em Elec. J.  Lin. Alg.}, 16: 183--186, 2007.


\enlargethispage{-10pt}

\bibitem{CdCM} B. Codenotti, G. Del Corso, and G. Manzini.  
Matrix rank and communication complexity.  
{\em Lin. Alg. Appl.}, 304: 193--200, 2000.


\bibitem{CdV} 	Y. Colin de Verdi\`ere. 
\newblock On a new graph invariant and a criterion for planarity.
\newblock In {\em Graph Structure Theory}, pp. 137--147, 
American Mathematical Society, Providence, RI, 1993.

\bibitem{CdV2} 	Y. Colin de Verdi\`ere. 
\newblock Multiplicities of eigenvalues and tree-width graphs.
\newblock {\em J. Comb. Theory B},
74: 121--146, 1998.


%\bibitem{Dthesis} L. A. Deaett. The positive semidefinite minimum 
%rank of a triangle-free graph.  Thesis (Ph.D.), The University of 
%Wisconsin - Madison, 2009.

\bibitem{Dea} L.  Deaett. The minimum semidefinite rank 
of a triangle-free graph. {\em Lin. Alg. Appl.} 434: 1945--1955, 2011.

\bibitem{Sri}
L. Deaett and V. Srinivasan.   Linear algebraic methods in communication complexity.  {\em Lin. Alg. Appl.}, 436: 4459--4472, 2012.

\bibitem{UOM} L. DeAlba, J. Grout, L. Hogben, R. Mikkelson, 
and K. Rasmussen.   Universally optimal matrices and field independence 
of the minimum rank of a graph.  {\em Elec. J.  Lin. Alg.}, 18: 403--419, 2009.

\bibitem{DHHHW} L.M. DeAlba, T.L.  Hardy, I.R. Hentzel, L. Hogben, 
and A. Wangsness. Minimum rank and maximum eigenvalue multiplicity of 
symmetric tree sign patterns. {\em Lin. Alg. Appl.}, 
418: 389--415, 2006.

\bibitem{small}	 L. DeLoss, J. Grout, L. Hogben, T. McKay, J. Smith, and G. Tims. 
Techniques for determining the minimum rank of a small graph.   
{\em Lin. Alg. Appl.} 432:   2995--3001, 2010.



%\bibitem[DGM]{SAGE}[DGM]	L. DeLoss, J. Grout, T. McKay, J. Smith, G. Tims. Program for calculating bounds on the minimum rank of a graph using \sage.   Available  at \url{http://arxiv.org/abs/0812.1616}. 
% and linked to the AIM workshop website \cite{AIMweb}.


\bibitem{DK} G. Ding and A. Kotlov.
\newblock On minimal rank over finite fields.
\newblock  {\it Elec. J.  Lin. Alg.},  15: 210--214,  2006.

\bibitem{EHHLR} C.J. Edholm, L. Hogben, M. Huynh, J. Lagrange, and D.D. Row. 
Vertex and edge spread of zero forcing number, maximum nullity, and 
minimum rank of a graph. {\em Lin. Alg. Appl.}, 436: 4352--4372, 2012.

\bibitem{EGR11} J. Ekstrand, C. Erickson, H.T. Hall, D. Hay, L. Hogben, R. Johnson, N. Kingsley, S. Osborne, T. Peters, J. Roat, A. Ross, D.D. Row, N. Warnberg, and M. Young.  Positive semidefinite zero forcing.  {\em Lin. Alg. Appl.}, 439: 1862--1874, 2013. 

\bibitem{EGR11a} J. Ekstrand, C. Erickson, D. Hay, L. Hogben, and J. Roat.  Note on positive semidefinite maximum nullity and positive semidefinite zero forcing number of partial 2-trees.  {\it Elec. J.  Lin. Alg.},  23: 79--97,  2012. 

\bibitem{FH}	S. Fallat and L. Hogben.
The minimum rank of symmetric matrices described by a graph: A survey.   
{\em Lin. Alg. Appl.} 426: 558--582, 2007.  



\bibitem{FP}
R. Fernandes and C. Perdigao. The minimum rank of matrices and the 
equivalence class graph. {\em Lin. Alg. Appl.} 
427: 161--170, 2007. 


\bibitem{Fied} 	M. Fiedler. 
\newblock A characterization of tridiagonal matrices.
\newblock {\em Lin. Alg. Appl.},
2: 191--197, 1969. 
\bibitem{F}	J. Forster.
A linear lower bound on the unbounded error probabilistic communication 
complexity.  
{\em J. Comp. Sys. Sci.}, 
65: 612--625, 2002.

\bibitem{Gol09} F. Goldberg.  On the Colin de Verdi\`ere numbers of Cartesian graph
products. {\em Lin. Alg. Appl.},  431: 2285--2290, 2009.

\bibitem{GB11} F. Goldberg and A. Berman.  On the Colin de Verdi\`ere number of graphs. {\em Lin. Alg. Appl.},  434:1656--1662, 2011.

\bibitem{Netal09OS} P. Hackney, B. Harris, M. Lay, L.H. Mitchell, 
S.K. Narayan, and A. Pascoe. Linearly independent
vertices and minimum semidefinite rank. {\em Lin. Alg. Appl.},  431: 1105--1115, 2009.

\bibitem{Hae81} W.H. Haemers. An upper bound for the Shannon capacity 
of a graph. In {\em Colloqua Mathematica
Societatis J\'anos Bolyai} 25 
(proceedings Algebraic Methods in Graph Theory, î Szeged, 1978), pp. 267--272, North-Holland, Amsterdam, 1981.

\bibitem{Hall} H.T. Hall. Minimum rank 3 is difficult to determine.  
Preprint.

\bibitem{HHMS}	H.T. Hall, L. Hogben, R. Martin, and B. Shader.
Expected values of parameters associated with the
minimum rank of a graph.  
{\em Lin. Alg. Appl.}, 
433: 101--117, 2010.

\bibitem{Hog05} L. Hogben.
\newblock Spectral graph theory and the inverse eigenvalue problem of a
graph.
\newblock  {\it Elec. J.  Lin. Alg.},  14: 12--31,  2005. 


\bibitem{Hogben} L. Hogben.
\newblock Orthogonal representations, minimum rank, and graph complements.
\newblock  {\it Lin. Alg. Appl.},  428: 2560--2568,  2008. 

\enlargethispage{-10pt}
\bibitem{cancun} L. Hogben.  Minimum rank problems.  
{\em Lin. Alg. Appl.}, 432: 1961--1974, 2010.

\bibitem{Hsp} L. Hogben.  A note on minimum rank and maximum 
nullity of  sign patterns. 
\newblock  {\it Elec. J.  Lin. Alg.},  22: 203--213, 2011.

\bibitem{HvdH06} L. Hogben and H. van der Holst.
\newblock Forbidden minors for the class of graphs $G$ with $\xi(G) \leq
2$.   {\em Lin. Alg. Appl.}, 423: 42--52, 2007.


\bibitem{HS} L. Hogben and B. Shader. Maximum generic nullity of a 
graph. {\em Lin. Alg. Appl.}, 432: 857--866, 2010.

\bibitem{vdH02}  H. van der Holst.  Graphs with magnetic Schr\"odinger operators
of low corank. {\em J. Comb. Theory B},  84: 311--339, 2002.   


\bibitem{vdH02b}	H. van der Holst.
On the ``Largeur d'Arborescence."   {\em J. Graph Theory}, 41: 24--52, 2002.

\bibitem{vdH03} H. van der Holst.  Graphs whose positive semi-definite matrices have nullity at most two. {\em Lin. Alg. Appl.}, 375: 1--11, 2003.   


\bibitem{vdH08twosep}	H. van der Holst.
The maximum corank of graphs with a 2-separation.   {\em Lin. Alg. Appl.} 428: 1587--1600, 2008.  

\bibitem{vdH08}	H. van der Holst.
Three-connected graphs whose maximum nullity  is at most three.   {\em Lin. Alg. Appl.} 429: 625--632, 2008.  

\bibitem{vdH09}  H. van der Holst. On the maximum positive semi-definite 
nullity
and the cycle matroid of graphs.
   {\em Elec. J.  Lin. Alg.}, 18: 192--201,  2009.


\bibitem{HLS} H. van der Holst, L. Lov\'asz, and A. Schrijver.
\newblock The Colin de Verdi\`ere graph parameter. 
\newblock In {\em Graph Theory and Computational Biology (Balatonlelle, 1996)}, pp. 29--85, 
%\newblock Mathematical Studies, 
Janos Bolyai Math. Soc., Budapest, 1999. 


\bibitem{Hsieh} L.-Y. Hsieh.  On minimum rank matrices having prescribed graph.  Ph.D. Thesis, University of Wisconsin-Madison, 2001.


\bibitem{Yeh} L.-H. Huang, G.J. Chang, and H.-G. Yeh.  On minimum rank 
and zero forcing sets of a graph. {\em Lin. Alg. Appl.}, 432: 2961--2973, 2010.

\bibitem{Yeh2} L.-H. Huang, G.J. Chang, and H.-G. Yeh.  A note on 
universally optimal matrices and field
independence of the minimum rank of a graph. {\em Lin. Alg. Appl.}, 433: 585--594, 2010.

%\bibitem[IMA10]{IMA}[IMA10] IMA-ISU research group on minimum rank (M. Allison,  
%E. Bodine,
%L. M.  DeAlba, 
%J. Debnath, L. DeLoss,
%C. Garnett,
%J. Grout, L. Hogben,
%B. Im,
%H. Kim,
%R. Nair,
%O. Pryporova,
%K. Savage,
%B.  Shader, 
%A. Wangsness Wehe).  Minimum rank of skew-symmetric matrices 
%described by a graph.   {\em Lin. Alg. Appl.}, 
%432: 2457--2472, 2010.

\bibitem{JMN}
Y. Jiang, L.H. Mitchell, and S.K. Narayan. 
Unitary matrix digraphs and minimum semidefinite rank.  
{\em Lin. Alg. Appl.}  428:1685--1695,  2008.



\bibitem{JL99} 	C.R. Johnson and A. Leal Duarte. The maximum 
multiplicity of an eigenvalue in a matrix whose graph is a tree. 
{\em Lin.  Multilin. Alg.}, 46: 139--144, 1999. 

  \bibitem{JL08} 	C.R. Johnson and J. Link. The extent to 
  which triangular sub-patterns explain minimum rank. 
  {\em Disc. Appl. Math.}, 156: 1637--1631, 2008.

\bibitem{JLS} C.R. Johnson, R. Loewy, and P. A. Smith.  The 
graphs for which the maximum multiplicity of an eigenvalue is two. 
{\em Lin.  Multilin. Alg.}, 57: 713--736, 2009. 




\bibitem{KR} 
S. Kopparty and K.P.S. Bhaskara Rao. The minimum rank problem: 
a counterexample. {\em Lin. Alg. Appl.} 428: 
1761--1765, 2008.


\bibitem{Kost} A.V. Kostochka. Lower bound of the Hadwiger number of graphs by their average degree  \textit{Combinatorica} {4}: 307--316, 1984.

\bibitem{KLV} A. Kotlov, L. Lov{\'a}sz, and S. Vempala. The Colin de Verd\`ere number and sphere representations of a graph.  \textit{Combinatorica} {17}: 483--521, 1997.

\bibitem{Lokam} S.V. Lokam, \emph{Complexity Lower Bounds using 
Linear Algebra}.
now Publishers Inc., Hanover, MA, 2009.

\bibitem{LSS89} L. Lov{\'a}sz, M. Saks, and A. Schrijver. Orthogonal 
representations and connectivity of graphs.  \textit{Lin. Alg. Appl.} {114/115}: 439--454, 1989.

\bibitem{LSS00} L. Lov{\'a}sz, M. Saks, and A. Schrijver. A correction: 
``Orthogonal representations and connectivity of graphs.'' 
\textit{Lin. Alg. Appl.} {313}: 101--105, 2000.

\bibitem{MS82} K. Mehlhorn and E.M. Schmidt.   Las Vegas is better 
than determinism in VLSI and distributed computing.
In {\em Proc. 14th Annual ACM Symposium on the Theory of Computing},  
pp.
330--337, 1982.
\enlargethispage{-10pt}
\bibitem{Mik} R.C. Mikkelson. Minimum rank of graphs that allow 
loops. Ph.D. Thesis, Iowa State University, 2008.

\bibitem{MNZ}
L.H. Mitchell, S. Narayan, and A. Zimmer.
Lower bounds in minimum rank problems.
{\em Lin. Alg. Appl.}, 432: 430--440, 2010.

\bibitem{Mit11}
L.H. Mitchell.
On the graph complement conjecture for minimum semidefinite rank.
{\em Lin. Alg. Appl.}, 435: 1311--1314, 2011.

\bibitem{MNZ2}
L.H. Mitchell, S. Narayan, and A. Zimmer.
Lower bounds for minimum semidefinite rank from orthogonal removal and chordal supergraphs.
{\em Lin. Alg. Appl.}, 436: 525-536, 2012.


\bibitem{N96}
P.M. Nylen,
Minimum-rank matrices with prescribed graph.
{\em Lin. Alg. Appl.}, 248: 303--316, 1996.  

\bibitem{Owe}
K. Owens.
Properties of the zero forcing number.
M.S. Thesis, Brigham Young University, 2009.

\bibitem{PS}
R. Paturi and J. Simon.
Probabilistic communication complexity.  {\em J. Comput.
Sys. Sci,}, 33: 106--123, 1984.

\bibitem{Peters}
T. Peters.
Positive semidefinite maximum nullity and zero forcing number.  
{\em Elec. J.  Lin. Alg.}, 23: 815--830,  2012.

\bibitem{RS} W.C. Rheinboldt and R.A. Shepherd. On a characterization of tridiagonal matrices by M.
Fiedler. {\em Lin. Alg. Appl.}, 8: 87--90, 1974.

\bibitem{Row} D.D. Row.
A technique for computing the zero forcing number of a graph
with a cut-vertex.
{\em Lin. Alg. Appl.}, 436: 4423--4432, 2012.


\bibitem{Sev}
S. Severini. Nondiscriminatory propagation on trees.
{\em J. Physics A}, 41: 482--002 (Fast Track Communication), 2008.

\bibitem{SINK} J. Sinkovic.  
Maximum nullity of outerplanar graphs and the path cover number.  
{\em Lin. Alg. Appl.}, 432: 2052--2060, 2010.

\bibitem{SvdH}
J. Sinkovic and H. van der Holst, 
The minimum semidefinite rank of the complement of partial $k$-trees,
{\em Lin. Alg. Appl.}, 434: 1468--1474, 2011

\bibitem{Tims}
G. Tims.
Haemers minimum rank.  
Ph.D. Thesis, Iowa State University, 2012.

 

\end{thebibliography}

